diffusion, websites with 1 pc

### 2022-06-06 src/level_lisa_la.Rmd
edits

path.out <- paste0(path,"/outputs/b_dist_centre_la.png")
ggplot(out.model.retail, aes(x=reorder(year, year), y=estimate)) +
           geom_errorbar(aes(ymin=conf.low, ymax=conf.high), 
                       width = 0.2,size  = 1,
                       position = "dodge", color="turquoise4") +
  #geom_hline(yintercept = 0, color = "red", size = 1) +
  geom_point() + coord_flip() +
  ylab("distance coefficient") + xlab("") + 
  ggtitle("Regression coefficients, distance to nearest city on website density, LA") +
  theme(plot.title = element_text(hjust = 0.5)) +
  ggsave(path.out)

>>>>

path.out <- paste0(path,"/outputs/b_dist_centre_la.png")
ggplot(out.model.retail, aes(x=reorder(year, year), y=estimate)) +
           geom_errorbar(aes(ymin=conf.low, ymax=conf.high), 
                       width = 0.2,size  = 1,
                       position = "dodge", color="turquoise4") +
  #geom_hline(yintercept = 0, color = "red", size = 1) +
  geom_point() + coord_flip() +
  ylab("distance coefficient") + xlab("") + 
  ggtitle("Regression coefficients, distance to nearest retail centre on website density, LA") +
  theme(plot.title = element_text(hjust = 0.5)) +
  ggsave(path.out)

### 2022-06-06 src/level_lisa_oa.Rmd
edits

path.out <- paste0(path,"/outputs/b_dist_centre_oa.png")
ggplot(out.model.retail, aes(x=reorder(year, year), y=estimate)) +
           geom_errorbar(aes(ymin=conf.low, ymax=conf.high), 
                       width = 0.2,size  = 1,
                       position = "dodge", color="turquoise4") +
  #geom_hline(yintercept = 0, color = "red", size = 1) +
  geom_point() + coord_flip() +
  ylab("distance coefficient") + xlab("") + 
  ggtitle("Regression coefficients, distance to nearest city on website density, OA") +
  theme(plot.title = element_text(hjust = 0.5)) +
  ggsave(path.out)

@@

```{r}
path.out <- paste0(path, "/outputs/r2_all.csv")

>>>>

path.out <- paste0(path,"/outputs/b_dist_centre_oa.png")
ggplot(out.model.retail, aes(x=reorder(year, year), y=estimate)) +
           geom_errorbar(aes(ymin=conf.low, ymax=conf.high), 
                       width = 0.2,size  = 1,
                       position = "dodge", color="turquoise4") +
  #geom_hline(yintercept = 0, color = "red", size = 1) +
  geom_point() + coord_flip() +
  ylab("distance coefficient") + xlab("") + 
  ggtitle("Regression coefficients, distance to nearest retail centre on website density, OA") +
  theme(plot.title = element_text(hjust = 0.5)) +
  ggsave(path.out)

@@

```{r}
path.out <- paste0(path, "/outputs/r2_all_oa.csv")
